MSDS6306_CaseStudy_2

### 2017-12-04 Presentation/MSDS6306_CaseStudy_2.Rmd
Indent Format
Indent Format

## 2_c_2_e To Clean up the data from Procrastination.csv: 
####      a. we converted the "Male" and "Female" that we found under the Column of "SonsCnt" and replaced it with the correct response of 1 = Male and 2 = Female. 
####      b. we rounded the PostHeldYrs to the nearest integer 
####      c. If the Annual Income was missing, we have converted it to -0.01 instead of 0. This will enable us to separate the true 0 from the missing values. 
####      d. Converted missing values in all the remaining Numeric fields to 0 
####      e. Converted missing values in all the Character fields to "Missing" 
####      f. Converted missing values in all the Factor fields to "Missing" 
####      g. If Country of Residence had values of 0, translated it to "Missing"
####      h. If the individual has held a position for more than 100 years, then convert it to 0 
####      i. If the current occupation is "0" or "Please Specify", then the data is treated as "Missing"
####      i. Standardized the Current Occupation for the Top 30 Key words.
####      k. Added columns for the individual’s average decisional procrastination (DP), procrastination behavior (AIP), generalized procrastination (GP), and life satisfaction (SWLS)
```{r 2_c_d_e_Data_Cleansing}
levels(ProcrastinationData$SonsCnt) <- c(levels(ProcrastinationData$SonsCnt), "1", "2")
ProcrastinationData$SonsCnt[ProcrastinationData$SonsCnt=='Male'] <- '1'
ProcrastinationData$SonsCnt[ProcrastinationData$SonsCnt=='Female'] <- '2'

>>>>

## 2_c_2_e To Clean up the data from Procrastination.csv: 
####      a. Converted the "Male" and "Female" that we found under the Column of "SonsCnt" and replaced it with the correct response of 1 = Male and 2 = Female. 
####      b. Rounded the PostHeldYrs to the nearest integer 
####      c. If the Annual Income was missing, we have converted it to -0.01 instead of 0. This will enable us to separate the true 0 from the missing values. 
####      d. Converted missing values in all the remaining Numeric fields to 0 
####      e. Converted missing values in all the Character fields to "Missing" 
####      f. Converted missing values in all the Factor fields to "Missing" 
####      g. If Country of Residence had values of 0, translated it to "Missing"
####      h. If the individual has held a position for more than 100 years, then convert it to 0 
####      i. If the current occupation is "0" or "Please Specify", then the data is treated as "Missing"
####      i. Standardized the Current Occupation for the Top 30 Key words.
####      k. Added columns for the individual’s average decisional procrastination (DP), procrastination behavior (AIP), generalized procrastination (GP), and life satisfaction (SWLS)
```{r 2_c_d_e_Data_Cleansing}
levels(ProcrastinationData$SonsCnt) <- c(levels(ProcrastinationData$SonsCnt), "1", "2")
ProcrastinationData$SonsCnt[ProcrastinationData$SonsCnt=='Male'] <- '1'
ProcrastinationData$SonsCnt[ProcrastinationData$SonsCnt=='Female'] <- '2'
